G\"{o}del's Ontological Proof of God's Existence (Draft)

### 2013-08-18 Natural Deduction/GodProof-ND.tex
Make definition numbers agree in Coq, ND and abstract

\textbf{Definitions:}
\begin{itemize}
\item \textbf{(D1)} A property is \emph{essential} for an individual if and only if it holds for that inidividual and necessarily entails every other property that holds for that individual: $\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))$
\end{itemize}

@@

\textbf{Definitions:}
\begin{itemize}
\item \textbf{(D2)} An individual is a \emph{God} if and only if he possesses all positive properties:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\item \textbf{(D3)} An individual \emph{necessarily exists} if and only if all its essential properties are necessarily witnessed:
$$
E(x) \biimp \all \varphi.[\ess{\varphi}{x} \imp \nec \ex x.\varphi(x)]
$$
\end{itemize}

>>>>

\textbf{Definitions:}
\begin{itemize}
\item \textbf{(D1)} An individual is a \emph{God} if and only if he possesses all positive properties:
$$
G(x) \biimp \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\item \textbf{(D2)} A property is \emph{essential} for an individual if and only if it holds for that inidividual and necessarily entails every other property that holds for that individual: $\ess{\varphi}{x} \biimp \varphi(x) \wedge \all \psi. (\psi(x) \imp \nec \all x. (\varphi(x) \imp \psi(x)))$
\end{itemize}

@@

\textbf{Definitions:}
\begin{itemize}
\item \textbf{(D3)} An individual \emph{necessarily exists} if and only if all its essential properties are necessarily witnessed:
$$
E(x) \biimp \all \varphi.[\ess{\varphi}{x} \imp \nec \ex x.\varphi(x)]
$$
\end{itemize}
